---
title: "Housing Prices"
author: "Dave Tang"
toc: true
number-sections: true
highlight-style: pygments
format:
  html:
    code-line-numbers: true
    code-fold: true
    html-math-method: katex
  docx: default
bibliography: references.bib
---

## Introduction

In this analysis, we build a model predicting sale prices of houses based on data on houses that were sold in the Duke Forest neighborhood of Durham, NC around November 2020. Let's start by loading the packages we'll use for the analysis.

```{r}
#| label: load-packages
#| code-summary: "Packages"
#| echo: false
#| warning: false
#| message: false

.libPaths('/packages')
my_packages <- c('openintro', 'tidyverse', 'knitr', 'broom')

using<-function(...) {
   # https://stackoverflow.com/a/44660688
   libs<-unlist(list(...))
   req<-unlist(lapply(libs,require,character.only=TRUE))
   need<-libs[req==FALSE]
   if(length(need)>0){
      install.packages(need)
      lapply(need,require,character.only=TRUE)
   }
}

using(my_packages)
```

We present the results of exploratory data analysis in @sec-eda and the regression model in @sec-model.

<!--# https://community.rstudio.com/t/insert-citations-in-non-visual-markdown-editor/94028 -->

We're going to do this analysis using literate programming [@knuth1984].

## Exploratory data analysis {#sec-eda}

The data contains `r nrow(duke_forest)` houses. As part of the exploratory analysis let's visualize and summarize the relationship between areas and prices of these houses.

### Data visualization

@fig-histogram shows two histograms displaying the distributions of `price` and `area` individually.

```{r}
#| label: fig-histogram
#| fig-cap: "Histograms of individual variables"
#| fig-subcap:
#|   - "Histogram of `price`s"
#|   - "Histogram of `area`s" 
#| layout-ncol: 2

ggplot(duke_forest, aes(x = price)) +
  geom_histogram(binwidth = 50000) +
  labs(title = "Histogram of prices")

ggplot(duke_forest, aes(x = area)) +
  geom_histogram(binwidth = 250) +
  labs(title = "Histogram of areas")
```

@fig-scatterplot displays the relationship between these two variables in a scatterplot.

```{r}
#| label: fig-scatterplot
#| fig-cap: "Scatterplot of price vs. area of houses in Duke Forest"

ggplot(duke_forest, aes(x = area, y = price)) +
  geom_point() +
  labs(title = "Price and area of houses in Duke Forest")
```

### Summary statistics

@tbl-stats displays basic summary statistics for these two variables.

```{r}
#| label: tbl-stats
#| tbl-cap: "Summary statistics for price and area of houses in Duke Forest"

duke_forest %>%
  summarise(
    `Median price` = median(price),
    `IQR price` = IQR(price),
    `Median area` = median(area),
    `IQR area` = IQR(area),
    `Correlation, r` = cor(price, area)
    ) %>%
  kable(digits = c(0, 0, 0, 0, 2))
```

## Modeling {#sec-model}

We can fit a simple linear regression model of the form shown in @eq-slr.

$$
price = \hat{\beta}_0 + \hat{\beta}_1 \times area + \epsilon
$$ {#eq-slr}

@tbl-lm shows the regression output for this model.

```{r}
#| label: tbl-lm
#| tbl-cap: "Linear regression model for predicting price from area"

price_fit <- lm(price ~ area, data = duke_forest)

price_fit %>%
  tidy() %>%
  kable(digits = c(0, 0, 2, 2, 2))
```

<!--# ADD CALLOUT HERE using the visual editor-->

::: callout-note
## This is a pretty incomplete analysis, but hopefully the document provides a good overview of some of the authoring features of Quarto!
:::

<!--# ADD SECTION HEADING FOR REFERENCES HERE -->

## References
